---
title: "Analysis of Pilot Data"
output:
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
---

```{r include = FALSE}
library(tidyverse)
library(lmerTest)
```

```{r, message = FALSE}
pilot <- here::here(
  "data",
  "processed_pilot.csv"
) %>% 
  read_csv() %>% 
  mutate(
    song = gsub(
      "audio/",
      "",
      stimulus_song
    )
  ) %>% 
  rename(
    target = target_song
  )
```

In this study we sampled `r nrow(distinct(pilot, pid))` participants, with each participant listening to `r max(pilot$trial_index+1)` 1 second exceprts. Participants rated each song in terms of the emotion they thought it expressed, it's valence, and it's arousal. 

# All song consdidered

From the table below we can see that over all songs 57% of happy targets were correctly identified and 48% of sad targfets were correctly identified
```{r}
correct_overall <- pilot %>% 
  group_by(target) %>% 
  summarise(correct = sum(correct)/n(),
            valence = mean(valence),
            arousal = mean(arousal))

correct_overall %>% 
  arrange(target) %>% 
  knitr::kable(format = "html") %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::scroll_box()
```

# Considering Happy, Sad, and Angry taget songs

```{r}
target_happy <- pilot %>% 
  select(target, song, correct, valence, arousal) %>% 
  filter(target == "happy") %>% 
  group_by(
    song
  ) %>% summarise(
    correct = sum(correct)/n(),
    valence = mean(valence),
    arousal = mean(arousal)
  ) %>% 
  arrange(correct)


target_happy  
```

Based of this I will retain the following songs as happy songs: 

- 21_Skank_Down.mp3
- 16_Restless.mp3
- 5_Get_Lucky.mp3
- 5_Valrie.mp3
- 1_Be_Happy.mp3.
- 26_Make_Light.mp3
  
I will find the mean correct for these songs to approximate a match with teh sad songs in terms of difficulty 

```{r}
selected_happy <- target_happy %>% 
  filter(
    song %in% c("21_Skank_Down.mp3", "26_Make_Light.mp3", "5_Valerie.mp3", "11_Be_Happy.mp3", "16_Restless.mp3", "5_Get_Lucky.mp3") 
  )

range(selected_happy$correct)
mean(selected_happy$correct)

```

  
```{r}
target_sad <- pilot %>% 
  select(target, song, correct, valence, arousal) %>% 
  filter(target == "sad") %>% 
  group_by(
    song
  ) %>% summarise(
    correct = sum(correct)/n(),
    valence = mean(valence),
    arousal = mean(arousal)
  ) %>% 
  arrange(correct) %>% 
  filter(correct > .25)


target_sad  
```

Based of this I will retain the following songs as sad songs: 

- 8_Fire_And_Rain_(LP_Version).mp3
- 3_Old_Blacktop.mp3	
- 7_Here_Today.mp3	
- 2_Love's_Requiem.mp3,
- 2_Inside.mp3
- 12_Skinny_Love.mp3

```{r}
selected_sad <- target_sad %>% 
  filter(
    song %in% c("8_Fire_And_Rain_(LP_Version).mp3", "3_Old_Blacktop.mp3", "15_Here_Today.mp3", "7_Here_Today.mp3", "2_Inside.mp3", "12_Skinny_Love.mp3") 
  )

range(selected_sad$correct)
mean(selected_sad$correct)
```


Here the ranges and means are as approximate as possible without duplicating songs. 

I also want to have angry target songs 

```{r}
target_angry <- pilot %>% 
  select(target, song, correct, valence, arousal) %>% 
  filter(target == "angry") %>% 
  group_by(
    song
  ) %>% summarise(
    correct = sum(correct)/n(),
    valence = mean(valence),
    arousal = mean(arousal)
  ) %>% 
  arrange(correct)


target_angry  
```

Here I will use 
- 13_Motown_Junk.mp3
- 2_Incomplete.mp3

```{r}
selected_angry <- target_angry %>% 
  filter(
    song %in% c("13_Motown_Junk.mp3", "2_Incomplete.mp3") 
  )

range(selected_angry$correct)
mean(selected_angry$correct)
```


Here a list of selected songs can be seen

```{r}
selected_songs <- pilot %>% 
  select(target, song, correct, valence, arousal) %>% 
  group_by(song) %>%
  summarise(
    valence = mean(valence),
    arousal = mean(arousal),
    target = target,
    correct = sum(correct)/n()
  ) %>% 
  filter(
    song %in% c("25_Old_Blacktop.mp3", "12_Fire_And_Rain_(LP_Version).mp3", "15_Here_Today.mp3", "2_Love's_Requiem.mp3", "2_Inside.mp3", "12_Skank_Down.mp3", "26_Make_Light.mp3", "28_Valerie.mp3", "11_Be_Happy.mp3", "16_Restless.mp3", "13_Motown_Junk.mp3", "2_Incomplete.mp3")
  ) %>% 
  distinct() %>% 
  arrange(target) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()

kableExtra::save_kable(
  selected_songs,
  here::here(
  "selected_songs_tab.html"
)
)

```

And here the songs can be seen plotted in terms of valence and arousal
```{r}
pilot %>% 
  select(target, song, correct, valence, arousal) %>% 
  group_by(song) %>%
  summarise(
    valence = mean(valence),
    arousal = mean(arousal),
    target = target,
    correct = sum(correct)/n()
  ) %>% 
  filter(
    song %in% c("25_Old_Blacktop.mp3", "12_Fire_And_Rain_(LP_Version).mp3", "15_Here_Today.mp3", "2_Love's_Requiem.mp3", "2_Inside.mp3", "12_Skank_Down.mp3", "26_Make_Light.mp3", "28_Valerie.mp3", "11_Be_Happy.mp3", "16_Restless.mp3", "13_Motown_Junk.mp3", "2_Incomplete.mp3")
  ) %>% 
  distinct() %>% 
  ggplot2::ggplot(
    aes(
      x = valence,
      y = arousal,
      shape = target,
      label = song,
      color = correct
    ) 
  )+
  geom_point() +
  theme_classic() +
  ggrepel::geom_text_repel() +
  coord_cartesian(xlim = c(1, 7), ylim = c(1, 7)) +
  ggplot2::ggtitle("Selected Songs plotted on Valence and Arousal") +
  scale_x_continuous(breaks = c(1:7)) +
  scale_y_continuous(breaks = c(1:7))
  

ggsave(
  here::here(
    "selected_songs_plt.png"
  )
)

```